\documentclass[12pt]{letter}

% Preamble

\usepackage[margin=1in]{geometry}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{fancyhdr, float, graphicx}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{fouriernc} % Use the New Century Schoolbook font
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{url}

\signature{Krishnaraj}
\address{Krishnaraj \\ Home}
\begin{document}


\begin{letter}{Mom and Dad \\ Home }
\opening{Dear Mom and Dad!}

I have been asked to write a letter to you to acknowledge how grateful I am to you, however, as seldom as I might say it outloud, 
I am always ever grateful to the both of you for everything I have. But this is a nice excuse for me to finally say \textit{how} grateful.\\

People always say that, parents bring kids into this world, and so they become their responsibilities. Which then means that anything
good that you do for them, is just that, \textit{your responsibility}. But I think that there is so much more to it. As I grow older and 
get to see the way that children throughout and in many parts of the world are treated after being born, it makes me a little more grateful
to know that it didnt happen to me, because you both made a conscious decision to make my life the way that it is. You chose to make my
childhood such that I dont have a single regret when I think back. Every time I hear about someone with childhood trauma, and realize that I am 
blessed to only have happy memories to look back to, I feel sorry for them, and all the more greatful to you. \\

I feel life is about the little things. It is the little things that show how much you love each other and the little things that 
stay stuck in our minds after years and years. But life is also about the big things that are spoken, but not realized. From paying for my school
and university fees, getting me the best medical treatment possible, getting me the best clothes, best devices, and anything that I can 
ask for, you haven't left a stone unturned in finding all the possible ways to make me happy, and my life better.\\

But the big things you see, is what everyone sees. The small things, not so much. You may not think that I notice everything, but I do.
You may not think I know that my presentations are on your desktop, dad, But I do. You may not think I notice how sad you are every time you miss
to make me my lunch, but I do. I do notice, you silently thanking God everytime you hear something good about me, I do hear every time 
you talk about me on the phone. I remember what you talked about me, and taught me while studying maths 7 years ago, what you told me yesterday, 
and the day before that, and every single thing that you have said to appreciat, scold, or advise me.\\
\vspace{1cm}

I am grateful for all those hours and hours of work that you put in everyday so that you could provide for me. I am grateful for the hours
and hours that you spent, trying to argue with me, trying to correct me, to understand me, and to nurture me. I am grateful for the hours and hours
that you sacrificed, when you decided to put me on the top of your priorities for years and years. I am grateful for the thousands of hours of fun, 
enjoyment, travel, movies, shows, and conversations, that you had with me, and for the thousands of hours of enjoyment, travel, movies, shows, 
and conversations that you \textit{chose not to have}, just so you could spend time with me. \\


Yeah its true that I may not always say everything out loud. Its true that I may not always speak my prayers out loud. But every time I have
sincerely closed my eyes, it has been for you. Its not that I dont like to express myself, but, I prefer to keep certain things to myself 
and myself only. Because I have learnt that while some things are best expressed, more things are best understood. And when it comes to my people
I just \dots expect them to understand. It doesnt however mean that I am not grateful, or that I would ever take you for granted. \\

When someone spends so much time and energy on something, they often expect appreciation for their work. They always expect something in return. 
Parenting however, you tell me, is no such thing. I agree, and I know that I cant do anything to ever repay what you have both done for me, given up
for me, sacrifices and overlooked for me, the efforts that you took, the difficult decisions that you made, or any of the other 146 things that you didnt
even think about doing because I was on the top of your priority list. But what I can do, is assure you that, none of that has gone unnoticed, 
and maybe you dont expect any appreciation, but none of that has gone unappreciated as well. I can assure that, no matter what happens, no matter 
where life takes me, you, us, or our family, you will never lose the son in me, and the son that you raised.\\   


You can only imagine there there is so much to write, that I never have to think before sitting down and writing this letter. The list just
goes on and on and on. As much as \textit{you} may not admit it, I owe everything I am to you. I do not believe in luck, and yet I am pretty lucky to have
been born into this family. \textit{From the bottom of my heart, and as genuinely as can be put in the form of words, Thank you, for everything, for all time, always.}\\





\flushleft{
	Yours Gratefully, \\
	Krishnaraj
}

\end{letter}
\end{document}

